### 2016-10-25 paper/evaluation.tex
Updated plots and eval

\Fix{TODO: MERGE VERY LONG INTO LONG}
To evaluate the frequency of time-consuming regression tests, we first
compiled the project and test source files, later, we measured the
elapsed time to run the tests via the build system ignoring
non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
resulting time from test executions into four different groups: tests
that ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{normal execution}), five to ten minutes (\emph{long
execution}), and more than ten minutes to execute (\emph{very long
execution}).  Figure~\ref{fig:piechart-time} shows the distribution
of subjects per group. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), normal
    execution ($1m \leq t < 5m$), long execution ($5m \leq t <
    10m$), and very long execution ($10m \leq t$).}
\end{figure}

We compared the execution time and number of tests for each subject. \Fix{...}

\begin{figure}[h!]%
    \centering
    \begin{minipage}{4.5in}%
        \subfigure[\Fix{normal}]{
            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
        }%
        \subfigure[\Fix{long}]{
            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-long.pdf}
        }\\
        \subfigure[\Fix{vlong}]{
            \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
        }%
    \end{minipage}
    \caption{\Fix{...}}
\end{figure}

>>>>

To evaluate the frequency of time-consuming regression tests, we first
compiled source and test files, later, we measured the elapsed time to
run the tests via the build system ignoring non-related tasks (\eg,
\emph{javadoc} generation).  We grouped the subjects according to the
execution time: tests that ran in less than one minute (\emph{short
execution}), one to five minutes (\emph{medium execution}), and more
than five minutes (\emph{long execution}).
Figure~\ref{fig:piechart-time} shows the proportion of subjects per
group. It is important to mention that Figure~\ref{fig:piechart-time}
represents a lower bound for elapsed time: some tests may finish early
due to a failure since the subjects were tested in a potentially
unstable revision.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), medium 
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).}
\end{figure}

For the subjects from the groups \emph{medium} and \emph{long}, we
compared the execution time and the number of tests successfully
executed. As expected, Figure~\ref{fig:scatters} reveals that the
number of tests cases are not related to the elapsed time.
\Fix{explain briefly what dominates a test execution/types of tests}.
We ignored outliers for better visualization.

\begin{figure}[h!]%
    \centering
    \begin{minipage}{0.5\textwidth}
        \subfigure[\Fix{medium}]{
            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-med.pdf}
        }\\
        \subfigure[\Fix{long}]{
            \includegraphics[width=\textwidth]{results/rq1/plots/scatterplot-long.pdf}
        }%
    \end{minipage}%
    \caption{\Fix{...use minutes instead of secs...}}%
    \label{fig:scatters}%
\end{figure}
